---
title: "data exploration"
format: gfm
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(dplyr)
library(stringr)
```

## Data Preview & First Looks

```{r}
#| label: amnesia
amnesia <- read_csv("data/amnesia.csv")
amnesia
```


```{r}
#| label: dloop
deathloop <- read_csv("data/deathloop.csv")
deathloop
```


First looks show some of the first areas I know I have to work around. I called up two games just to confirm that they both look the same. Both have the same almost metadata-like details at the top that will have to be excluded, and both (and all the rest) of the files have that one odd issue, with the column name being the game's steam id (used to pull the reviews in through the script)

```{r}
#| label: dloop-colnames
print(colnames(deathloop))
```

## Early Tidying Steps

### colnames


```{r}
#| label: dloopcols
deathloop <- deathloop |>
  rename(review_id = ...1, language = 2, date = ...3, review_type = ...4, purchased = ...5, score = ...6, upvotes = ...7, review = Reviews, engtxt = ...9) |>
  filter(language == 'english')
```

Thinking about future column names! Not yet thinking deeply about what columns I'll ultimately drop, but I'm starting to weigh my options (date, upvotes, engtxt)

Note: Think about how to rename cols using iteration for ease.... the language column name comes from the game url id number used to pull the reviews. 


### str replace


```{r}
#| label: loop-reviews
deathloop |>
  distinct(review_type)
```

```{r}
#| label: loop-replace
deathloop |>
  mutate(review_type =  str_replace_all(review_type, 
                c("✅" = "POS",
                  "❌" = "NEG")))
```

For now, going with POS and NEG for easy visual differences. I found "positive" and "negative" too messy and similar looking at a glance, I think POS and NEG are easier to quickly tell apart. 


## Game Info DFs


```{r}
#| label: overpos
overpos <- tibble(game = c("Outer wilds", "Stardew Valley", "Hades", "Chants of Sennaar", "The Case of the Golden Idol"), rank = "Overwhelmingly Positive", perc_positive = c("95%", "98%", "98%", "98%", "98%"), year = c("2020", "2016", "2020", "2023", "2022"), total_reviews = c("75,534", "797,573", "264,668", "22,874", "8,107"), eng_reviews = c("45,703", "363,715", "133,152", "10,464", "5,778"), price = c("$25", "$15", "$25", "$20", "$18"),  steam_id = c("753640", "413150", "1145360", "1931770", "1677770"))
overpos

```


```{r}
#| label: verypos
verypos <- tibble(game = c("Disco Elysium", "Superliminal", "The Stanley Parable: Ultra Deluxe", "Dead Space 2", "Night in the Woods"), rank = "Very Positive", perc_positive = c("92%", "94%", "94%", "94%", "94%"), year = c("2019", "2020", "2022", "2011", "2017"), total_reviews = c("105,914", "25,549", "30,300", "22,870", "16,570"), eng_reviews = c("52,174", "13,202", "22,192","10,723", "12,697"), price = c("$40", "$20", "$25", "$20", "$20"), steam_id = c("632470", "1049410", "1703340", "47780", "481510"))
verypos
```


```{r}
#| label: pos
pos <- tibble(game = c("Powerful Courses", "Bike Ride 3D", "Tomorrow is my Birthday", "Hyper Space", "Ascending Inferno"), rank = "Positive", perc_positive = c("100%", "100%", "100%", "100%", "100%"), year = c("2023", "2024", "2024", "2024", "2024"), total_reviews = c("49", "49", "48", "33", "48"), eng_reviews = c("37", "43", "42","15", "53"), price = c("$15", "$4", "$3", "$5", "$15"), steam_id = c("2092330", "2607330", "2940020", "2444290", "2442820"))
pos
```


```{r}
#| label: mostlypos
mostlypos <- tibble(game = c("Ranch Simulator", "Resident Evil 6", "Dark Pictures Anthology: Little Hope", "Blair Witch", "Final Fantasy VIII Remastered"), rank = "Mostly Positive", perc_positive = c("80%", "79%", "73%", "78%", "73%"), year = c("2023", "2013", "2020", "2019", "2019"), total_reviews = c("32,194", "41,151", "6,068", "5,898", "4,174"), eng_reviews = c("9,373", "12,266", "2,713","2,761", "2,421"), price = c("$25", "$20", "$20", "$30", "$20"), steam_id = c("1119730", "221040", "1194630", "1092660", "1026680"))
mostlypos
```


```{r}
#| label: mixed
mixed <- tibble(game = c("Deadly Premonition: The Director's Cut", "Silent Hill Homecoming", "Redfall", "Amneisa: A Machine for Pigs", "Vampire: The Masquerade - Coteries of New York"), rank = "Mixed", perc_positive = c("66%", "47%", "41%", "68%", "69%"), year = c("2013", "2008", "2023", "2013", "2019"), total_reviews = c("3,072", "2,379", "2,380", "6,807", "2,113"), eng_reviews = c("1,976", "1,099", "1,629","4,178", "1,266"), price = c("$25", "$40", "$40", "$20", "$20"), steam_id = c("247660", "19000", "1294810", "239200", "1096410"))
mixed
```


```{r}
#| label: mostlyneg
mostlyneg <- tibble(game = c("Roller Coaster Tycoon World", "Urban Empire", "Postal 3", "Towns", "Edge of Space"), rank = "Mostly Negative", perc_positive = c("25%", "34%", "39%", "27%", "32%"), year = c("2016", "2017", "2011", "2012", "2015"), total_reviews = c("3,179", "1,902", "4,328", "2,381", "1,945"), eng_reviews = c("1,944", "892", "1,984","2,058", "2,428"), price = c("$15", "$30", "$6", "$15", "$15"), steam_id = c("282560", "352550", "10220", "221020", "238240"))
mostlyneg
```


```{r}
#| label: neg
neg <- tibble(game = c("Bridge!", "Damned Nation Reborn", "Hazen: The Dark Whispers", "At Home", "Girl with a big SWORD"), rank = "Negative", perc_positive = c("12%", "10%", "20%", "18%", "16%"), year = c("2011", "2015", "2010", "2019", "2018"), total_reviews = c("47", "83", "48", "44", "43"), eng_reviews = c("31", "48", "41","26", "35"), price = c("$5", "$13", "$9", "$5", "$2"), steam_id = c("300160", "345710", "46730", "1048640", "946600"))
neg
```


```{r}
#| label: veryneg
veryneg <- tibble(game = c("Lords of the Black Sun", "Skyscraper Simulator", "Citadels", "Construction Machines 2014", "Bhop Pro"), rank = "Very Negative", perc_positive = c("18%", "14%", "13%", "7%", "17%"), year = c("2014", "2010", "2013", "2014", "2020"), total_reviews = c("328", "266", "490", "239", "244"), eng_reviews = c("300", "479", "276","156", "69"), price = c("$25", "$3", "$15", "$7", "$10"), steam_id = c("246940", "252910", "238870", "252050", "1308950"))
veryneg
```



```{r}
#| label: overneg
overneg <- tibble(game = c("Kinetic Void", "Spacebase DF9", "FlatOut 3 Chaos & Destruction", "Command & Conquer 4 Tiberian Twilight", "Superpower 3"), rank = "Overwhelmingly Negative", perc_positive = c("17%", "17%", "17%", "16%", "10%"), year = c("2014", "2014", "2011", "2010", "2022"), total_reviews = c("1,553", "4,313", "4,079", "4,711", "4,713"), eng_reviews = c("1,346", "3,675", "1,606","2,625", "2,626"), price = c("$10", "$10", "$10", "$20", "$30"), steam_id = c("227160", "246090", "201510", "47700", "1563130"))
overneg
```



```{r}
#| label: gamesdf
allgames <- bind_rows(overpos, verypos, pos, mostlypos, mixed, mostlyneg, neg, veryneg, overneg)
allgames
```


```{r}
#write_csv(allgames, file="0-gameinfo.csv")
```




### Some quick stats

45 total games, how many reviews will I be looking at? 

```{r}
#| label: reviews-total
allgames <- allgames |>
  mutate(total_reviews = (str_replace_all(total_reviews, ",", ""))) |>
  mutate(total_reviews = as.numeric(total_reviews))
  
sum(allgames$total_reviews)

```

```{r}
#| label: eng-total
allgames <- allgames |>
  mutate(eng_reviews = (str_replace_all(eng_reviews, ",", ""))) |>
  mutate(eng_reviews = eng_reviews |>
           na_if("NA")) |>
  mutate(eng_reviews = as.numeric(eng_reviews))
  
sum(allgames$eng_reviews, na.rm=TRUE)
```

I only plan to look at english reviews, but it took some work to transform both columns into something sum-able. Take note that, at this time, some of the english reviews rows are NA because steam did not list a difference between "total" and "english", I get the feeling this happens when there aren't many reviews total (since it mostly appears with the less well-reviewed games). 

I'll have to import the datasets myself, get a count of how many rows are noted to be in English, and come back here to update the dataframes for later. 


## Getting the Data read in

So this is where I've been noodling around trying to get all my data read in. It's still very much a work in progress, but here's the scraps of what I've been putting together and working on here and there.


```{r}
#| label: list-files
filenames <- list.files("data", pattern="*.csv", full.names=TRUE)
filenames
```


```{r}
#| label: dupe-check
file1 <- readLines("data/command.csv")

file2 <- readLines("data/athome.csv")

are_identical_nearly <- all.equal(file1, file2)
print(paste("Nearly identical:", are_identical_nearly))

```

```{r}
#| label: dupe-check2
check_c <- read_csv("data/command.csv")
check_c

check_d <- read_csv("data/bigsword.csv")
check_d
```




There we go, the failure caused by dreaded column 2

```{r}
#| label: readfiles
#| eval: FALSE
read_csv(filenames)
```


Here's where I was experimenting with a for loop to go through each file, add it into an empty list, and then I could bind that list together, but that wasn't working either. 


```{r}
#| label: file-loop
#| eval: FALSE
datalist <- list()

for (file in filenames) {
  gamefile <- read.csv(file, header=FALSE)
  datalist <- gamefile
}
```


The loop is obviously working, but the dfs aren't being added to the list. Looking at the example below, it's only going through and saving the last dataset (Vampire Masquerade)

```{r}
#| label: boundgames
#| eval: FALSE
testing <- rbind(datalist)

testing
```

```{r}
#| label: vampires
read.csv("data/vampires.csv")
```


Here are the notes from 10/28 on a new process I'm going to give a shot! We'll see how it gets going. 



look at chapter 26

pipe into map create anon function in map \x() to pull the column title into its own column


x<- listfiles

x|>
map(\(x))
  x|> steam ID col 
    take steam id from col 2 |>
    mutate(steam_id = IDNO))|>
    rename(review_lang = 2) |>
    bindrows()
    
    LETTERS[1:9]
    
    
    lines <- read_lines(file)
    steam_id <- str (parse to steam id) (lines)
    data <- read_csv(lines[26:length(lines)])
    
    (lines[26:length(lines)]) turn this into a single string before putting into read_csv
    
    
    |> mutate(steam_id = steam_id)
    

```{r}
#| label: find-colname
numtest <- amnesia |> 
  select(2) |>
  colnames()

numtest
```

```{r}
#| label: id-col
amnesia <- amnesia |>
  mutate(steam_id = numtest)

amnesia
```


```{r}
#| label: mod-readlines
lines <- read_lines(filenames)
data <- read_csv(filenames, lines[25:length((lines))])


data
```





## Building function


```{r}
#| label: df-function
build_df <- function(x){
  gamelines <- read_lines(x)
  flatlines <- str_flatten(gamelines, "\n")
  games_df <- read_csv(flatlines)
  steam_id <- games_df |> select(2) |> colnames()
  games_df <- games_df |> mutate(steam_id = steam_id)
  games_df <- games_df |>
    rename(review_id = 1, language = 2, date = 3, review_type = 4, purchased = 5, score = 6, upvotes = 7, review = 8, engtxt = 9) |>
  filter(language == 'english')
}
```


```{r}
#| label: build-df
games_df <- build_df(filenames)
games_df
```


```{r}
#| label: reviews-csv
#write_csv(games_df, file="private/reviews.csv")
```






```{r}
#| label: id-verify
games_df |>
  distinct(steam_id)
```







```{r}
#| label: sample-df
dlooplines <- read_lines("data/amnesia.csv")
flatlines <- str_flatten(dlooplines, "\n")
colid <- read_csv(flatlines)
steam_id <- colid |> select(2) |> colnames()
colid <- colid |> mutate(steam_id = steam_id)
colid <- colid |>
  rename(review_id = ...1, language = 2, date = ...3, review_type = ...4, purchased = ...5, score = ...6, upvotes = ...7, review = Reviews, engtxt = ...9) |>
  filter(language == 'english')

colid
```





```{r}
#| label: scratch
#| eval: FALSE
filenames |>
      map(\(x) read_csv(x, show_col_types=FALSE, col_names = c("A", "B", "C", "D", "E", "F", "G", "H", "I"))) |>
      map(\(x) 
        x |>
          mutate(steam_id = colnames(x)[2]) |>
          rename(review_lang = 2) 
      ) |>
 head(2)


#colid[-(1:24),] |>


#dlooplines2 <- dlooplines[24:length((dlooplines))]
#dloopstr <- str_flatten(dlooplines2, "\n")
#dloopdata <- read_csv(dloopstr)
```


