---
title: "analysis pipeline"
format: gfm
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
```

**Note**: reviews.csv is too large to upload to github right now, but using the data which is uploaded and the "data exploration" file, if you un-comment the write_csv chunk, you should be able to recreate it just fine. You'll just have to change the file path to read in for this one. 


```{r}
#| label: readingin
reviews_df <- read_csv("../private/reviews.csv")
reviews_df
```

```{r}
#| label: game-ids
reviews_df |>
  distinct(steam_id)
```


## Cleaning Up


```{r}
#| label: posneg
reviews_df <- reviews_df |>
    mutate(review_type =  str_replace_all(review_type, 
                c("✅" = "POS",
                  "❌" = "NEG")))
```


Fix those pesky emoji columns (I'm going to ditch the "purchased" column later on, so I didn't bother)

```{r}
#| label: reviews-df
reviews_df
```


```{r}
#| label: colchecks
diffrows <- reviews_df[reviews_df$review != reviews_df$engtxt, ]
diffrows
```

The engtxt column is not actually different from the review column, (it seems to auto translate the only difference being conversions of any reviews that just say "xx%" (100% being converted to 1) or anything with x/10 being also converted to a string of numbers. Since it's essentially the same data, I'll ditch the engtxt column and keep the review one.

Now for column decisions. I'll keep review_id since it's a unique value for each different review. 

I don't know that the date column is extremely important. I might want to look at how quickly games get reviews (are they concentrated at release and fall off, or is it relatively steady? any spikes?) but I will probably edit the column to a better format. Ditch the time, look into whatever format works best in R. 

I don't think the purchased col is extremely important, it only marks if a review writer has purchased the game or not, which is not key to any of my analysis.

score and upvotes are based on user response to a comment. Users can upvote for helpfulness of a review, or mark it as funny. I can't find data on how exactly the review score is calculated, but I don't think these two factors will play a huge role in what I'm looking to do. 


```{r}
#| label: reviews-df2
#narrowing the df down to only the columns I want
reviews_df <- reviews_df |>
  select(review_id:review_type, review, steam_id)
reviews_df
```

Now, I wanted to verify everything is correct. If every review ID is unique and I didn't accidentally duplicate anything, then piping the review_id column into distinct() should be the exact same dimensions as the full dataframe.

I had to run some fixes, but it's all good now!


```{r}
#| label: rowscheck
reviews_df |>
  distinct(review_id)
```


## List of Goals

- adjust the date column (DONE)
- clean up the text of non text items (IN PROGRESS)
- Word tokens and word count per review
- word types
- TTR

**Early Exploration**

- average review length
- most common words (with and without stop words)
- most common words for pos and for neg
- some stats (correlation) - length and review type, review and rating type, maybe some others
- TF-IDF

**Later Goals**

- build a classifier

## Date column

Date format as is: 2025.08.29 02:05

  - remove timestamp
  - reformat
  - change column class

```{r}
#| label: datecol
reviews_df <- reviews_df |>
  mutate(date = str_replace_all(date, "(\\d{4})\\.(\\d{2})\\.(\\d{2}).*", "\\1-\\2-\\3"))
reviews_df$date <- as.Date(reviews_df$date)  
  
reviews_df
```


## Text Cleaning

```{r}
#| label: review-text
reviews_df |>
  select(review)
```


```{r}
#| label: text-replace
reviews_df <- reviews_df |>
   mutate(review =  str_replace_all(review, 
                c("\n" = " ",
                  "\\(" = "",
                  "\\)" = "",
                  "(\\w)/(\\w)" = "\\1 \\2",
                  "(\\w) / (\\w)" = "\\1 \\2",
                  "\\[.*?\\]" = "",
                  "⠸|⢹|⠣|⣛|⣣|⣁|⣖|⣭|⠃|⢻|⣧|⣽" = "",
                  "⣷|⣟|⢶|⢣|⠄|⡿|⣮|⣻|⣦|⢛|⠿|⢭|⠼|⢀" = "",
                  "⡉|⣶|⠘|⢿|⡠|⢆|⣳|⡵|⡅|⠙|⣼|⡄|⡧|⢇" = "",
                  "⣴|⣌|⢽|⠻|⡛|⣤|⡝|⣾|⠚|⣀|⠏|⡻|⢘|⠎" = "",
                  "⣝|⣸|⣰|⡆|⣱|⣡|⢟|⣯|⡟|⢠|⠑|⠛|⢸|⢯" = "",
                  "⢎|⣕|⡮|⠝|⡾|⡯|⠕|⡹|⡂|⢈|⠟|⠢|⣎" = "",
                  "⡪|⡱|⢔|⡑|⢊|⢊|⠠|⠡|⠈|⡌|⠪|⣺|⡽" = "",
                  "⣗|⢉|⢄|⣐|⢂|⢐|⡔|⡀|⠁|⢑|⢨|⡁" = "",
                  "⢮|⣆|⠐|⣫|⢷|⢮|⢗|⢪|⣬|⢜|⢾|⣞" = "",
                  "⢗|⠥|⠨|⢪|⠂|⣬|⡗|⠧|⢞|⣪|⢱|⣬" = "",
                  "⡨|⡷|⢚|⠹|⡎|⢥|⠀|⡺|⢌|⡊|⡡|⠱|⠌" = "",
                  "⡲|⣹|⣑|⣨|⢳|⢡|⣜|⢵|⣔|⡸|⡭|⢃" = "",
                  "⢴|⢕|⡇|⢬|⢅|⣵|⠮|⢏|⡒|⡫|⡐|⡳" = "",
                  "⠯|⢢|⡩|⣃|⠔|⠜|⠇|⠅|⣇|⡰|⠰|⣅" = "",
                  "⡘|⡃|⢰|⡬|⡜|⢝|⢩|⡢|⡼|⣘|⠬|⠊|⢤" = "",
                  "⠫|⢼|⡕|⣲|⡏|⢺|⡈|⠤|⣥|⡥|⠶|⠽|⣥|⢦" = "",
                  "⠩|⡍|⠵|⣉|⣚|⠴|⠭|⣓|⡋|⠗|⣄|⣈|⠍" = "",
                  "⠺|⣢|⠷|⠋|⠾|⣠|⡴|⠆|⢖|⠞|⢲|⢁|⠉|⢋" = "",
                  "⢧|⣂|⢙|⠳|⣏|⡣|⡞|⠒|⡶|⣩|⠓|⣍|⠲|⡤" = "",
                  "⢫|⣙|⣊|⠖|⠦|⡙|⢓|⡦|⣒|⢒|⢍|⢒|⣋|⣋|⡖|⣿|⡚|⡓" = "",
                  "▄|░|┌|┼|▐|▀|▓|╝|╔|▌|╗|╚|═|║|▒|Ñ|│|∩|╓|╫" = "",
                  "╙|╡|╠|⊙|▅|┤|●|▂|▃|◥|█" = "",
                  
                  

                  "──+" = "─",
                  "__+" = "_",
                  
                  "  +" = " "
                  
                  )
                
                
                ))
```


I'm doing some exploring using str_view to dive in and look at what I want to get rid of to begin some real analysis. 

First - do I want to lowercase before tokenizing? I think yes but I have to recheck old homeworks to be sure. Definitely want to lowercase before looking at types and before doing tf-idf.

  - how do you make a set of word types in R anyway i don't know
  - probably by using unique() doy
  
Second - what to do with punctuation? I have to review previous work also.
  
For the sake of processing text, I'm first removing any parenthesis included. it could be interesting what gets put in a parenthetical statement vs outside, but for pure analysis and vectorizing we don't want them. 

There are some included kind of html(?) tags like [b] and [/b] of [h1] etc. I want to get rid of those too. 

Getting rid of /, sometimes it appears as word/word and others word / word. Replacing it with a space and will later process to move extra spaces down to one space
  - sometimes it appears in 7/10 or something. I'm keeping those but I have to think about what to do with it. It also depends on how the tokenizer handles it. If it tokenizes to [7] [/] [10] I think that's acceptable.

```{r}
grep -c -P


```



Questions - what do to with emojis? 

Sometimes they are used stylistically to split up reviews:
📚 Story / Narrative, ⌛ Length, 🔁 Replayability

Other times functionally (this is about difficulty):
🔲 Too easy
☑️ Casual-friendly
🔲 Balanced/Normal
🔲 Challenging
🔲 Brutal but fair
🔲 Pure chaos (PvP focus)

Sometimes in place of words:
At least one review, start to finish, contains one item only 💩
Another one looks like: This game is 💩 but i still love it

Some reviews also have no words and will just say "7/10" and nothing else, what about those? 

What about abbreviations? I've seen af, wtf, omg, lmao, etc etc. 
  - there are a lot, i imagine just leave them as they are

There are also emoticons in the old style: :D, xD etc
I even saw ° ͜ʖ ͡°, ﾉ◕ヮ◕ﾉ*:･ﾟ✧

LOTS of formatting choices people make for visual purposes:
=====, ☑ and ☐ (not as emojis), 

Or what about this...
There are a number of reviews using ⣿ (and all the variations in the replace text chunk above) to create a kind of ASCII art that can be safely removed, it is not speech information at all.

Think about \\{.*?\\} - there are some unicodes that show up I was having trouble singling out so I have to figure that out. I think they're probably special characters used in some more elaborate emoticons/faces that didn't quite translate somewhere along the way. 

links? Lots of people are linking to things in their reviews.


```{r}
#| label: text-search
str_view(reviews_df$review, "/")
```


## Tokenizing

Testing out the tokenizing here to see if there's anything I need to change in the text cleanup chunk above before I move onto an analysis qmd

unnest tokens
you can mess with formatting if needed to select how you want things to tokenize

