---
title: "4-stretch-goals"
format: html
---

These are some aspects of my work that I ultimately decided to move to a sort of "stretch goals" of the project. Elements I was interested in but weren't necessarily pertinent to the analysis I was focused one. Or, in the case of emojis usage, elements I Was interested in but didn't strictly have the R know-how to get working exactly how I wanted. 

I also used a specific emoji usage measurement that would not render from a qmd with gfm format, and required that I use html format. Rather than do that to my entire analysis notebook, I decided to isolate the emoji usage details here instead. 

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(tidytext)
library(ggplot2)
library(highcharter)
library(palmerpenguins)
library(tidyr)
library(scales)
library(ggplot2)
```

**Note**: Please run [0-data-exploration](https://github.com/Data-Sci-2025/Steam-Reviews-Analysis/blob/main/data_processing/0-data-exploration.qmd) and [1-data-cleanup](https://github.com/Data-Sci-2025/Steam-Reviews-Analysis/blob/main/data_processing/1-data-cleanup.qmd) first to create the version of the .csv file needed to start here.


```{r}
#| label: readingin
reviews_df <- read_csv("../private/reviews_analyze.csv", show_col_types = FALSE)
```


### Reviews over time

```{r}
#| eval: false
ggplot(dat, aes(x=Date_Published)) +   stat_count(geom='line', aes(y=..count..))
```





## Emojis

A lot of work went into keeping those emojis, so I want to take a look at them! 

```{r}
#| label: emoji-str
emoji_pattern <- "[\\\U0001F600-\\\U0001F64F\\\U0001F300-\\\U0001F5FF\\\U0001F900-\\\U0001F9FF\\\U00002600-\\\U000027BF]"
```


```{r}
#| label: extract-emojis
emojis <- reviews_df |>
  filter(grepl(emoji_pattern, types, perl=TRUE)) |>
  mutate(types = str_remove_all(types, "\\w|,|'|‘|’
                                 %|\\.|’|\\\036|－|❝|❞
                                 |‑"))

emojis
```


Only 1,622 of our reviews contain some kind of emoji usage. Not as many as I expected!


```{r}
#| label: emojis-only
emoji_df <- emojis |>
  mutate(types = sapply(emojis$types, remove_dupes)) |>
  count(types, sort=TRUE)

emoji_df
```


```{r}
#| label: plot-emoji
#| eval: FALSE
max_count <- emoji_df |>
  pull(n) |>
  max()


hchart(
  emoji_df, 
  "bar",
  hcaes(types, n), 
  name = "Count",
  # dataLabels = list(enabled = TRUE, style = list(fontWeight = "normal"))
  ) |>
  hc_xAxis(
    min = 0,
    max = 30,
    scrollbar = list(enabled = TRUE)
    ) |>
  hc_yAxis(
    max = max_count,
    title = list(
      text = "Count",
      align = "high"
      )
    ) |>
  hc_tooltip(
    headerFormat = "{point.key}",
    pointFormat = " {point.y}"
  ) |>
  hc_size(height = 700)
```


Cool [source](https://jkunst.com/blog/posts/2021-01-10-using-emoji-with-highcharterhighcharts/) for the emoji finding & charting code.



## Language Choices

Swear word detection??





